Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-11 cosmic_voids.tex
done section 2, new figure filenames, moved simulation section

\documentclass[a4,useAMS,usenatbib,usegraphicx]{latex/mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
\include{latex/macros}

@@

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
In Section  \ref{sec:simulations} we describe the N-body simulation we
use to test our algorithm. 
In Section \ref{sec:bulk_voids} we explain in detail our void finder
based on the fractional anisotropy of the tidal and shear tensor
fields. 
Our results are presented in \ref{sec:results} to finally comment and
conclude about these findings in Section \ref{sec:conclusions}.

%*************************************************************************
\section{Algorithms to label the Cosmic Web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

%-------------------------------------------------------------------------
\subsection{The tidal web (Tweb)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

This scheme was initially proposed by \citet{Hahn07} as an
alternative for classifying the Cosmic Web based on the tidal tensor.
The tidal tensor allows a classification in terms of the orbital
dinamics of the matter field
This approach extends to second-order the equations of motion around 
local minima of the gravitational potential. 
The second-order term corresponds to the tidal tensor, which is
defined as the Hessian matrix of the normalized gravitational
potential.

@@

Since the tidal tensor can be represented by a real and  symmetric
$3\times 3$ matrix, it is always possible to diagonalize  
it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
\lambda_3$ with its corresponding eigenvectors ${\bf u}_{1}$, ${\bf u}_{2}$,
${\bf u}_{3}$. 
This set of eigenvalues are indicators of the local  orbital stability
in each direction ${\bf u}_i$, which is to label the Cosmic Web.
The number of positive (stable) or negative (unstable) eigenvalues allows 
to label a location into one of the next four types of environment: 
voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
A modification to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. The relative strength 
of each eigenvalue is no longer defined by the sign, but instead by a
threshold value $\lambda_{\rm th}$ that can be tuned in such a way
that the visual impression of the web-like matter distribution is
reproduced.

%-------------------------------------------------------------------------
\subsection{The velocity web (Vweb)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematic scheme to define the Cosmic Web environment in 
the simulation, which has been thoroughly described in 
\cite{Hoffman12}.
This scheme has been used to study the shape, spin and peculiar
velocity alignments of dark matter halos with the cosmic web
\citep{Libeskind13,Forero2014}. 
We refer the reader to these papers to find a detailed description of
the algorithm, its limitations  and capabilities.    
The Vweb scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. This tensor is given by the 
following expression

%.........................................................................
%V-Web Definition
\eq{V_web}
{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}},}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. Like the tidal tensor, 
$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
matrix with real values, making it possible to find three real
eigenvalues and its corresponding eigenvectors.
%$\lambda_{1}\geq\lambda_{2}\geq\lambda_3$.
%whose sum (the 
%trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
%local velocity field smoothed on the physical scale ${\mathcal R}$.

In this case we also use the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ to classify the cosmic web
in the four web types we have already described.

Usually, the threshold is a free parameter that is tuned to reproduce
the visual appearence of the comic web. 
In this paper we take a different approach.
We find the optimal value of the threshold based on the maximization
of the fractional anisotropy field in the locations label as filaments
and walls.

\section{Numerical Simulations}
\label{sec:simulations}

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy degree of a diffusion process, e.g. 
the diffusivity of water molecules through cerebral tissue in nuclear
magnetic resonance imaging. 
Here we propose the FA, much in the same way as \citet{Libeskind13},
as a tracer of cosmic voids.

The FA is defined as follows.
%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} },}
%.........................................................................
where the eigenvalues are taken from either the Tweb or the Vweb 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, FA$=0$ 
corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
and FA$=1$ with a highly anisotropic distribution.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). 
  Middle column. Components of the Cosmic Web using $\lambda_{th}$
  values that put an upper bound of $FA=0.95$ to voids. Voids
  corresponds with white, sheets to gray, filaments to dark gray and
  knots with black regions. 
  Right column. Sketches the distribution of the catalogued voids by
  our method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/FA_L1.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/delta_L1.pdf}

  \captionof{figure}{\small Distributions of the FA (left panel) and the 
  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
  for each web scheme (Tweb, red lines. Vweb, blue lines) as calculated 
  over all cells of the grid. Thick central lines correspond with the median 
  and filled regions with the $50\%$ of the distribution.}

@@

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the Tweb and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells $FA<0.95$.   
The middle column in Fig. \ref{fig:FA_field} shows the web
classification for this choice of $\lambda_{th}$, demonstrating that
it is a sensible choice to define voids.

@@

@@

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogues. FA-Tweb (red curves), FA-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

@@

Since the shape of the voids exhibit a wide range of geometries, a common 
way to represent their size is through the equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. As mentioned before, we applied a threshold merger
in order to avoid void hierarchization, what means we are working with the
top hierarchy of voids. We limit our findings to voids with effective radius
greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
Below that scale numerical resolution effects becomes important. We find a
volume filling fraction of voids of $54.88\%$ of the total volume of the 
simulation for the FA-Tweb and $47.06\%$ for the FA-Vweb.

In Fig. \ref{fig:volume_function} we show the void size distributions
for both schemes and for the overall distribution of voids as well as for 
overcompensated and subcompensated void subsamples. The central region of
the distributions ($3$\hMpc\ -- $6$\hMpc), exhibit an approximately flat 
shape, contrary to expected from highly non-linear structures like dark 
matter halos, where the abundances increase for smaller structures. 
The distribution of the FA-Tweb is consistent with a two-barrier problem 
\citep{Sheth04}: formation of large voids is inhibited by the 
\textit{void-in-void} problem (first barrier), where large voids are 
constituted hierarchically of smaller ones. In turn, formation of small 
voids is damped by the \textit{void-in-cloud} problem (second barrier), 
where nearby collapsing structures limit the abundance of embedded small 
voids.

The FA-Vweb scheme does not tackle properly the \textit{void-in-cloud} 
problem as it predicts large abundances of smaller voids. However, an 
interesting result is the difference between the overcompensated and 
subcompensated subsamples. Subcompensated voids, which are expected to 
be embedded in low-density regions like walls and larger voids, exhibit
smaller abundances compatible with the result of the FA-Tweb. Then, the 
most dramatic contribution to the overabundance of small voids for the 
FA-Vweb comes from overcompensated voids. This implies that, although
nearby non-linear structures squeeze out embedded smaller voids, the
rapid and isotropic collapse in these zones, along with the more rugged 
nature of the velocity field make these voids still detectable by this 
scheme.

@@

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_VwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_TwebFAG1.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_density_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_velocity_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_FA_VwebFAG1.pdf}

@@

\bibliographystyle{latex/mn2e}
\bibliography{references}

%.........................................................................
%FIGURE -: FA of some regions and shape illustration
%\begin{flushleft}
%\begin{figure*}
%\centering
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
%  width=0.3\textheight]{./figures/FA_Prolatenes.png}

%  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
%  random sample of cells (left panel) and for different spherical 
%  geometries (right panel). For the cells, each environment is coded with
%  a different colour, i.e. voids corresponds with dark blue points, 
%  sheets with green, filaments with orange and knots with cyan. The axis 
%  of the spheroids are computed from the relative strengths of the 
%  eigenvalues, so their shape sketch the relative expanding/collapsing 
%  dynamics into each direction.}

%  \label{fig:FAShapeness}
%  \vspace{0.1 cm}

%\end{figure*}
%\end{flushleft}
%.........................................................................
\end{document}

>>>>

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
%\usepackage[section]{placeins}
\usepackage {graphicx}
%\usepackage{graphics}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}

%=========================================================================
%		INTERNAL MACROS
%=========================================================================
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
%SAMPLES
\newcommand{\GHBDM}{\texttt{GH}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\GHFOF}{\texttt{GH}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\IHBDM}{\texttt{IH}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\IHFOF}{\texttt{IH}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\PBDM}{\texttt{P}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\PFOF}{\texttt{P}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\IPBDM}{\texttt{IP}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\IPFOF}{\texttt{IP}$_{\mbox{\tiny{FOF}}}$ }
\newcommand{\RIPBDM}{\texttt{RIP}$_{\mbox{\tiny{BDM}}}$ }
\newcommand{\RIPFOF}{\texttt{RIP}$_{\mbox{\tiny{FOF}}}$ }

%MY COMMANDS #############################################################
\newcommand{\sub}[1]{\mbox{\scriptsize{#1}}}
\newcommand{\dtot}[2]{ \frac{ d #1 }{d #2} }
\newcommand{\dpar}[2]{ \frac{ \partial #1 }{\partial #2} }
\newcommand{\pr}[1]{ \left( #1 \right) }
\newcommand{\corc}[1]{ \left[ #1 \right] }
\newcommand{\lla}[1]{ \left\{ #1 \right\} }
\newcommand{\bds}[1]{\boldsymbol{ #1 }}
\newcommand{\oiint}{\displaystyle\bigcirc\!\!\!\!\!\!\!\!\int\!\!\!\!\!\int}
\newcommand{\mathsize}[2]{\mbox{\fontsize{#1}{#1}\selectfont $#2$}}
\newcommand{\eq}[2]{\begin{equation} \label{eq:#1} #2 \end{equation}}
\newcommand{\lth}{$\lambda_{th}$ }
\newcommand{\reff}{{\ifmmode{r_{\mbox{\tiny eff}}}\else{$r_{\mbox{\tiny eff}}$}\fi}}
%#########################################################################

@@

This paper is organized as follows. 
In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
we use to find the cosmic web in N-body simulations. 
In Section \ref{sec:bulk_voids} we explain in detail our void finder
based on the fractional anisotropy of the tidal and shear tensor
fields. 
In Section  \ref{sec:simulations} we describe the N-body simulation we
use to test our algorithm. 
Our results are presented in \ref{sec:results} to finally comment and
conclude about these findings in Section \ref{sec:conclusions}.

%*************************************************************************
\section{Algorithms to find the Cosmic Web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

In next two subsections we describe the major features of the two
algorithms (T-web and V-web) we use to find and classify the cosmic web in cosmological
N-body simulations. 
These schemes have also been used to develop other kind of studies
such as the alignment of the shape, spin and peculiar velocity of dark
matter halos with the cosmic web \citep{Libeskind13,Forero2014}.
We refer the reader to the paper of \cite{Forero09} and
\cite{Hoffman12} to read a detailed description of each algorithm.

%-------------------------------------------------------------------------
\subsection{The tidal web (T-Web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

This scheme was initially proposed by \citet{Hahn07} as an
alternative for classifying the Cosmic Web based on the tidal tensor.
The tidal tensor allows a classification in terms of the orbital
dinamics of the matter field.
This approach extends to second-order the equations of motion around 
local minima of the gravitational potential. 
The second-order term corresponds to the tidal tensor, which is
defined as the Hessian matrix of the normalized gravitational
potential.

@@

Since the tidal tensor can be represented by a real and  symmetric
$3\times 3$ matrix, it is always possible to diagonalize  
it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
\lambda_3$ with its corresponding eigenvectors ${\bf u}_{1}$, ${\bf u}_{2}$,
${\bf u}_{3}$. 
The eigenvalues are indicators of the local  orbital stability
in each direction ${\bf u}_i$. 
The sign of the eigenvalues can be used to classify the Cosmic Web.
The number of positive (stable) or negative (unstable) eigenvalues allows 
to label a location into one of the next four types of environment: 
voids (3 negative eigenvalues), sheets (2), filaments (1) and knots (0).

A modification to this scheme was introduced by \citet{Forero09}
by means of a relaxation of the stability criterion. 
The relative strength  of each eigenvalue is no longer defined by the
sign, but instead by a threshold value $\lambda_{\rm th}$ that can be
tuned in such a way that the visual impression of the web-like matter
distribution is reproduced.

%-------------------------------------------------------------------------
\subsection{The velocity web (V-Web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematic scheme to define the Cosmic Web environment in 
the simulation introduced by \cite{Hoffman12}.
The V-web scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. This tensor is given by the 
following expression

%.........................................................................
%V-Web Definition
\eq{V_web}
{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}},}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. Like the tidal tensor, 
$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
matrix with real values, making it possible to find three real
eigenvalues and its corresponding eigenvectors.

In this case we also use the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ to classify the cosmic web
in the four web types already mentioned.

Usually, the threshold is a free parameter that is tuned to reproduce
the visual appearence of the comic web. 
In this paper we take a different approach.
We find the optimal value of the threshold based on the maximization
of the fractional anisotropy field in the locations label as filaments
and walls. 
This is described in detailed in the next Section.

@@

The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
conceived to quantify the anisotropy degree of a diffusion process, e.g. 
the diffusivity of water molecules through cerebral tissue in nuclear
magnetic resonance imaging. 
Here we present the FA, much in the same way as \citet{Libeskind13},
to use it as a tracer of cosmic voids.

The FA is defined as follows.
%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} },}
%.........................................................................
where the eigenvalues can be taken from either the T-web or the Vweb 
(FA-T-web and FA-Vweb respectively). Such as it is defined, FA$=0$ 
corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
and FA$=1$ with a highly anisotropic distribution.

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). 
  Middle column. Components of the Cosmic Web using $\lambda_{th}$
  values that put an upper bound of $FA=0.95$ to voids. Voids
  corresponds with white, sheets to gray, filaments to dark gray and
  knots with black regions. 
  Right column. Sketches the distribution of the catalogued voids by
  our method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{FA_L1.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{delta_L1.pdf}

  \captionof{figure}{\small Distributions of the FA (left panel) and the 
  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
  for each web scheme (T-web, red lines. Vweb, blue lines) as calculated 
  over all cells of the grid. Thick central lines correspond with the median 
  and filled regions with the $50\%$ of the distribution.}

@@

From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
conclude that the FA is a good tracer of voids as it is almost perfectly
correlated with low values of $\lambda_1$. 
We propose that voids should be composed completely by regions of
FA$<0.95$.
If we increase the values of $\lambda_1$ from its minimum until it
we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
correspond to critical values of $\lambda_{1}^T = 0.265$ and
$\lambda_{1}^V = 0.175$ for the T-web and Vweb, respectively.
This means that setting $\lambda_{th}$ to either
$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
all the cells $FA<0.95$.   
The middle column in Fig. \ref{fig:FA_field} shows the web
classification for this choice of $\lambda_{th}$, demonstrating that
it is a sensible choice to define voids.

@@

\section{Numerical Simulation}
\label{sec:simulations}

@@

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{voids_regions_volume_all.pdf}

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogues. FA-T-web (red curves), FA-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

@@

Since the shape of the voids exhibit a wide range of geometries, a common 
way to represent their size is through the equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. As mentioned before, we applied a threshold merger
in order to avoid void hierarchization, what means we are working with the
top hierarchy of voids. We limit our findings to voids with effective radius
greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
Below that scale numerical resolution effects becomes important. We find a
volume filling fraction of voids of $54.88\%$ of the total volume of the 
simulation for the FA-T-web and $47.06\%$ for the FA-Vweb.

In Fig. \ref{fig:volume_function} we show the void size distributions
for both schemes and for the overall distribution of voids as well as for 
overcompensated and subcompensated void subsamples. The central region of
the distributions ($3$\hMpc\ -- $6$\hMpc), exhibit an approximately flat 
shape, contrary to expected from highly non-linear structures like dark 
matter halos, where the abundances increase for smaller structures. 
The distribution of the FA-T-Web is consistent with a two-barrier problem 
\citep{Sheth04}: formation of large voids is inhibited by the 
\textit{void-in-void} problem (first barrier), where large voids are 
constituted hierarchically of smaller ones. In turn, formation of small 
voids is damped by the \textit{void-in-cloud} problem (second barrier), 
where nearby collapsing structures limit the abundance of embedded small 
voids.

The FA-Vweb scheme does not tackle properly the \textit{void-in-cloud} 
problem as it predicts large abundances of smaller voids. However, an 
interesting result is the difference between the overcompensated and 
subcompensated subsamples. Subcompensated voids, which are expected to 
be embedded in low-density regions like walls and larger voids, exhibit
smaller abundances compatible with the result of the FA-T-Web. Then, the 
most dramatic contribution to the overabundance of small voids for the 
FA-Vweb comes from overcompensated voids. This implies that, although
nearby non-linear structures squeeze out embedded smaller voids, the
rapid and isotropic collapse in these zones, along with the more rugged 
nature of the velocity field make these voids still detectable by this 
scheme.

@@

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_TwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_VwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_TwebFAG1.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_VwebFAG1.pdf}

@@

\bibliographystyle{mn2e}
\bibliography{references}

\end{document}
